Team size and composition in home health care

### 2023-10-19 paper-presentation/paper-presentation.qmd
Minor

# generates image of productivity cdf vs total scheduled workers
# targets(list): all (cdf) values to be evaluated: i.e. all x's to Pr(P <= x)
# p: probability a worker is present on scheduled moment
# max_M: upper limit of x-axis (maximum scheduled workers)
# min_M: lower limit of x-axis (minimum scheduled workers) 
def plot_productivity(targets,p,min_M,max_M,pinned_size):
    fig, ax = plt.subplots(figsize=(12,5))
    M = np.arange(min_M, max_M)

>>>>

# generates image of productivity cdf vs total scheduled workers
# targets(list): all (cdf) values to be evaluated: i.e. all x's to Pr(P <= x)
# p: probability a worker is present on scheduled moment
# max_M: upper limit of x-axis (maximum scheduled workers)
# min_M: lower limit of x-axis (minimum scheduled workers) 
def plot_productivity(targets,p,min_M,max_M,pinned_size):
    fig, ax = plt.subplots(figsize=(10,6))
    M = np.arange(min_M, max_M)
